paper_pdf

### 2020-03-21 paper_pdf.Rmd
Adding more poisson details

```{r, include= FALSE}
subset_2 <- data[c(6:11, 13:14, 16:17, 19:22, 24, 26:28)]
poisson_reg <- glm(`Students eligible for FLP per thousand` ~ ., data  = subset)
summary(poisson_reg)
```
```{r, include = FALSE}
stargazer::stargazer(poisson_reg, single.row = FALSE, no.space = TRUE)
```
\begin{table}[!htbp] \centering 
  \caption{} 
  \label{} 
\begin{tabular}{@{\extracolsep{5pt}}lc} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
 & \multicolumn{1}{c}{\textit{Dependent variable:}} \\ 
\cline{2-2} 
\\[-1.8ex] & `Students eligible for FLP per thousand` \\ 
\hline \\[-1.8ex] 
 `Grocery stores per thousand` & $-$1.055 \\ 
  & (1.014) \\ 
  `Supercenters per thousand` & $-$19.318$^{*}$ \\ 
  & (10.034) \\ 
  `Convenience stores per thousand` & $-$0.256 \\ 
  & (0.713) \\ 
  `Specialized stores per thousand` & 1.603 \\ 
  & (2.765) \\ 
  `Fast food restaurants per thousand` & 0.762 \\ 
  & (0.758) \\ 
  `Full service restaurants per thousand` & $-$1.383$^{***}$ \\ 
  & (0.437) \\ 
  `\% of students eligible for FLP` & 2.489$^{***}$ \\ 
  & (0.024) \\ 
  `Per capita WIC redemptions` & 0.417$^{***}$ \\ 
  & (0.028) \\ 
  `Per capita SNAP benefits` & 0.354$^{***}$ \\ 
  & (0.041) \\ 
  `Acres of vegetables harvested per thousand` & 0.005$^{***}$ \\ 
  & (0.001) \\ 
  `Recreation facilities per thousand` & $-$5.774$^{**}$ \\ 
  & (2.755) \\ 
  `Persistent Poverty indicator` & 2.141$^{**}$ \\ 
  & (0.847) \\ 
  `Child Poverty rate` & $-$0.683$^{***}$ \\ 
  & (0.051) \\ 
  `Persistent Child Poverty Indicator` & 1.382$^{**}$ \\ 
  & (0.698) \\ 
  `Metropolitan Area indicator` & 0.379 \\ 
  & (0.466) \\ 
  `Milk price in cents` & $-$0.091$^{***}$ \\ 
  & (0.018) \\ 
  `Low access adults per thousand` & $-$0.143$^{***}$ \\ 
  & (0.004) \\ 
  `Low access children per thousand` & 0.645$^{***}$ \\ 
  & (0.016) \\ 
  Constant & 3.149$^{*}$ \\ 
  & (1.844) \\ 
 \hline \\[-1.8ex] 
Observations & 3,065 \\ 
Log Likelihood & $-$11,590.200 \\ 
Akaike Inf. Crit. & 23,218.410 \\ 
\hline 
\hline \\[-1.8ex] 
\textit{Note:}  & \multicolumn{1}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
\end{tabular} 
\end{table}

>>>>

```{r, include= FALSE}
subset_2 <- data[c(6:11, 13:14, 16:17, 19:22, 24, 26:28)]
poisson_reg <- glm(`Students eligible for FLP per thousand` ~ ., data  = subset_2)
summary(poisson_reg)
```
```{r, include = FALSE}
stargazer::stargazer(poisson_reg, single.row = FALSE, no.space = TRUE)
```
\begin{table}[!htbp] \centering 
  \caption{} 
  \label{} 
\begin{tabular}{@{\extracolsep{5pt}}lc} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
 & \multicolumn{1}{c}{\textit{Dependent variable:}} \\ 
\cline{2-2} 
\\[-1.8ex] & `Students eligible for FLP per thousand` \\ 
\hline \\[-1.8ex] 
 `Grocery stores per thousand` & $-$1.055 \\ 
  & (1.014) \\ 
  `Supercenters per thousand` & $-$19.318$^{*}$ \\ 
  & (10.034) \\ 
  `Convenience stores per thousand` & $-$0.256 \\ 
  & (0.713) \\ 
  `Specialized stores per thousand` & 1.603 \\ 
  & (2.765) \\ 
  `Fast food restaurants per thousand` & 0.762 \\ 
  & (0.758) \\ 
  `Full service restaurants per thousand` & $-$1.383$^{***}$ \\ 
  & (0.437) \\ 
  `\% of students eligible for FLP` & 2.489$^{***}$ \\ 
  & (0.024) \\ 
  `Per capita WIC redemptions` & 0.417$^{***}$ \\ 
  & (0.028) \\ 
  `Per capita SNAP benefits` & 0.354$^{***}$ \\ 
  & (0.041) \\ 
  `Acres of vegetables harvested per thousand` & 0.005$^{***}$ \\ 
  & (0.001) \\ 
  `Recreation facilities per thousand` & $-$5.774$^{**}$ \\ 
  & (2.755) \\ 
  `Persistent Poverty indicator` & 2.141$^{**}$ \\ 
  & (0.847) \\ 
  `Child Poverty rate` & $-$0.683$^{***}$ \\ 
  & (0.051) \\ 
  `Persistent Child Poverty Indicator` & 1.382$^{**}$ \\ 
  & (0.698) \\ 
  `Metropolitan Area indicator` & 0.379 \\ 
  & (0.466) \\ 
  `Milk price in cents` & $-$0.091$^{***}$ \\ 
  & (0.018) \\ 
  `Low access adults per thousand` & $-$0.143$^{***}$ \\ 
  & (0.004) \\ 
  `Low access children per thousand` & 0.645$^{***}$ \\ 
  & (0.016) \\ 
  Constant & 3.149$^{*}$ \\ 
  & (1.844) \\ 
 \hline \\[-1.8ex] 
Observations & 3,065 \\ 
Log Likelihood & $-$11,590.200 \\ 
Akaike Inf. Crit. & 23,218.410 \\ 
\hline 
\hline \\[-1.8ex] 
\textit{Note:}  & \multicolumn{1}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
\end{tabular} 
\end{table}
